---
title: "Moduls"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## by Atajan Arashev

---
title: "Modules"
output: github_document

---
#KARKAVELRAJA J. (Updated a Year Ago). Amazon Sales Dataset, Version 1.0. Retrieved [Date Retrieved] from https://www.kaggle.com/datasets/karkavelrajaj/amazon-sales-dataset.

```{r setup2}
knitr::opts_chunk$set(echo = TRUE)

library(mclust)
library(ggplot2)
library(dplyr)
library(tidyr)
library(tm)         
library(sentimentr) 
library(wordcloud)
library(cluster)  
library(RColorBrewer)
library(dplyr)

```




```{r summary}


# Reading and Initial Inspection of the Data
amazon_data <- read.csv("amazon.csv", stringsAsFactors = FALSE)
str(amazon_data)
head(amazon_data)
summary(amazon_data)
column_names <- names(amazon_data)
print(column_names)



```

### Visualization: Log-Transformed Discounted Price Distribution
```{r Price Distribution}
### Visualization: Log-Transformed Discounted Price Distribution

library(ggplot2)

# Check for missing values
print(sum(is.na(amazon_data)))

# Data Cleaning
amazon_data$discounted_price <- as.numeric(gsub("₹|,", "", amazon_data$discounted_price))
amazon_data$actual_price <- as.numeric(gsub("₹|,", "", amazon_data$actual_price))

# Convert the columns to numeric type
amazon_data$discounted_price <- as.numeric(amazon_data$discounted_price)
amazon_data$actual_price <- as.numeric(amazon_data$actual_price)




# Visualization: Log-Transformed Discounted Price Distribution
amazon_data$discounted_price_log <- log1p(amazon_data$discounted_price)
ggplot(amazon_data, aes(x = discounted_price_log)) +
  geom_histogram(binwidth = 0.1, fill = "blue", color = "black") +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "Log-Transformed Discounted Price Distribution",
       x = "Log-Transformed Discounted Price", y = "Count") +
  theme_minimal()








```

### Categorical Data Analysis



### Rating Analysis
```{r Rating Analysis}
library(dplyr)
library(ggplot2)
# Convert the 'rating' column to numeric, coercing any non-numeric values to NA
amazon_data$rating <- as.numeric(as.character(amazon_data$rating))
# Impute NAs with the median rating
median_rating <- median(amazon_data$rating, na.rm = TRUE)
amazon_data$rating[is.na(amazon_data$rating)] <- median_rating
# Enhanced Violin Plot for Rating Analysis
ggplot(amazon_data, aes(x = factor(0), y = rating)) +
  geom_violin(trim = FALSE, fill = "#00A08A") +
  geom_jitter(width = 0.1, color = "darkgray", alpha = 0.5) +
  scale_y_continuous(limits = c(1, 5)) +  # Set limits assuming ratings are between 1 and 5
  labs(title = "Distribution of Product Ratings on Amazon", x = "", y = "Rating") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.title = element_text(hjust = 0.5))
```



### Relationship Between Ratings and Prices


```{r Rating Discount}
# Enhanced scatter plot with improved visualization
ggplot(amazon_data, aes(x = rating, y = discounted_price)) +
  geom_point(alpha = 0.2, size = 2, aes(color = discounted_price)) +  # Adjust alpha and size, add color scale
  scale_color_gradient(low = "blue", high = "red") +  # Gradient color from low to high price
  geom_smooth(method = "lm", color = "black", se = FALSE) +  # Change color for better contrast
  scale_y_log10(labels = scales::comma) +  # Log-transform y-axis
  labs(
    title = "Relationship Between Ratings and Discounted Price",
    subtitle = "Data points are colored from low (blue) to high (red) prices.",
    x = "Rating",
    y = "Discounted Price (log scale)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",  # Hide legend if color is not meaningful
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),  # Center and bold title
    plot.subtitle = element_text(hjust = 0.5, size = 10),  # Center subtitle
    axis.text = element_text(size = 12),  # Adjust axis text size
    axis.title = element_text(size = 12)  # Adjust axis title size
  )
#The graph seems to suggest that product price does not necessarily increase with higher ratings. Products with high ratings can have a wide range of prices, and similarly, lower-rated products also span a broad range of prices. The log scale on the y-axis helps to visualize the full range of prices without letting the highest prices dominate the graph's visual space.

```
```{r category_count}



# Display the plot
ggsave("category_count_plot.png", width = 12, height = 8, dpi = 300)



# Perform the data manipulation and create the plot
category_count <- amazon_data %>%
  group_by(category) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count))

ggplot(category_count, aes(x = reorder(category, -Count), y = Count)) +
  geom_bar(stat = "identity", fill = "#0073C2FF") +
  theme_minimal() +
  labs(title = "Product Count by Category in Amazon Listings",
       x = "Category",
       y = "Product Count") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1, size = 12),
        axis.title = element_text(size = 14),
        title = element_text(size = 16)) +
  theme(legend.position = "none")






```

```{r ANOVA}

# You've already read the data
amazon_data <- read.csv("amazon.csv", stringsAsFactors = FALSE)
# Convert 'rating' to numeric, handling non-numeric values
amazon_data$rating <- as.numeric(as.character(amazon_data$rating))
# Check for and handle NA values
sum(is.na(amazon_data$rating))  # Check how many NAs are there
amazon_data <- na.omit(amazon_data)  # Remove rows with NAs
# Perform ANOVA test
# Ensure that 'category' is a factor if it's not
amazon_data$category <- as.factor(amazon_data$category)

anova_result <- aov(rating ~ category, data = amazon_data)
summary(anova_result)



```











### Linear Regression Model
```{r LR Model}
# Set the working directory (this line is optional if you've already set the working directory in R)


# Load necessary libraries
library(dplyr)

# Read the data
amazon_data <- read.csv('amazon.csv', stringsAsFactors = FALSE)

# Data cleaning steps
amazon_data$discounted_price <- as.numeric(gsub("₹|,", "", amazon_data$discounted_price))
amazon_data$rating <- as.numeric(as.character(amazon_data$rating))

# Drop rows with NA values in 'rating' or 'discounted_price'
amazon_data <- na.omit(amazon_data)

# Extract the main category from the 'category' column
amazon_data$category_main <- sapply(strsplit(amazon_data$category, split = "\\|"), `[`, 1)

# Convert 'category_main' to a factor
amazon_data$category_main <- as.factor(amazon_data$category_main)

# Ensure there are at least two levels in 'category_main'
if (length(levels(amazon_data$category_main)) < 2) {
  stop("Not enough levels in 'category_main' to fit the model.")
}

# Fit the linear regression model
lm_model <- lm(discounted_price ~ rating + category_main, data = amazon_data)

# Print the summary of the linear model
summary(lm_model)


```

# # Word Cloud Generation
```{r Word Cloud}
library(wordcloud)
library(tm)

# Text Preprocessing
corpus <- Corpus(VectorSource(amazon_data$about_product))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("en"))
corpus <- tm_map(corpus, stripWhitespace)

# Create a term-document matrix
dtm <- TermDocumentMatrix(corpus)

# Calculate word frequencies
word_freqs <- sort(rowSums(as.matrix(dtm)), decreasing = TRUE)
word_freqs_df <- data.frame(word = names(word_freqs), freq = word_freqs)

# Create the word cloud
set.seed(1234)
wordcloud(words = word_freqs_df$word, freq = word_freqs_df$freq, min.freq = 1,
          max.words = 100, random.order = FALSE, rot.per = 0.25,
          colors = brewer.pal(8, "Dark2"))

```
#### K-means Clustering rating discount_price
```{r  K-means}

# Clustering Analysis
# Preparing Data for Clustering
clustering_data <- na.omit(amazon_data[, c('rating', 'discounted_price')])
clustering_data <- scale(clustering_data)


# K-means Clustering
set.seed(123)
kmeans_result <- kmeans(clustering_data, centers = 3)
print(kmeans_result$centers)
```
#KMEANS SAMPLE SIZES
```{r SAMPLE SIZES}

print(kmeans_result$size )
```

###Optimal Cluster Count Determination via Silhouette Analysis
```{r Silhouette}
clustering_data <- na.omit(amazon_data[, c('rating', 'discounted_price')])
clustering_data <- scale(clustering_data)


# K-means Clustering
set.seed(123)
kmeans_result <- kmeans(clustering_data, centers = 3)
print(kmeans_result$centers)

# Calculate silhouette scores for different numbers of clusters
silhouette_scores <- sapply(2:10, function(k) {
  km.res <- kmeans(clustering_data, centers = k, nstart = 25)
  # You need a distance matrix for the silhouette function
  diss <- dist(clustering_data)
  silhouette_score <- silhouette(km.res$cluster, diss)
  mean(silhouette_score[, "sil_width"])
})

# Print the silhouette scores
print(silhouette_scores)

library(ggplot2)

# Assuming silhouette_scores has been correctly computed as shown in your script
silhouette_df <- data.frame(
  k = 2:10,
  silhouette_score = silhouette_scores
)

# Plotting the silhouette scores
ggplot(silhouette_df, aes(x = k, y = silhouette_score)) +
  geom_line(color = "blue", size = 1) +  # Set line color and size
  geom_point(color = "red", size = 3) +  # Set point color and size
  labs(title = "Average Silhouette Score for Different Numbers of Clusters",
       x = "Number of Clusters", y = "Average Silhouette Score") +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(c(-1, 1))  # Set y-axis limits




```


###GMM
```{r GMM}
clustering_data <- na.omit(amazon_data[, c('rating', 'discounted_price')])
clustering_data <- scale(clustering_data)

# Set a more reasonable range for the number of clusters
G_range <- 1:10

# Calculate BIC for a range of number of clusters and plot
BIC_values <- mclustBIC(clustering_data, G = G_range)
plot(BIC_values, what = "BIC")

# Select the number of clusters with the best BIC value within the range
optimal_model <- which.max(BIC_values)

# Fit the GMM model with the selected number of clusters
gmm_model <- Mclust(clustering_data, G = optimal_model)

# Summary of the GMM model
summary(gmm_model)

```


###GMM and 2D Scatter Plot of GMM Clusters
```{r GMM2D}

clustering_data <- na.omit(amazon_data[, c('rating', 'discounted_price')])
clustering_data <- scale(clustering_data)

# Set a more reasonable range for the number of clusters
G_range <- 1:10

# Calculate BIC for a range of number of clusters and plot
BIC_values <- mclustBIC(clustering_data, G = G_range)
plot(BIC_values, what = "BIC")

# Select the number of clusters with the best BIC value within the range
optimal_model <- which.max(BIC_values)

# Fit the GMM model with the selected number of clusters
gmm_model <- Mclust(clustering_data, G = optimal_model)

# Summary of the GMM model
summary(gmm_model)

# Visualize the classification from GMM
plot(gmm_model, what = "classification")
# Load the necessary libraries
library(ggplot2)

# Assuming 'gmm_model' is your fitted Gaussian Mixture Model object and 'clustering_data' is your data
clusters <- gmm_model$classification
num_clusters <- max(clusters)

# Convert the scaled matrix to a data frame and set column names
clustering_data_df <- as.data.frame(clustering_data)
colnames(clustering_data_df) <- c('rating', 'discounted_price')

# Generate a set of distinct colors, one for each cluster
colors <- grDevices::rainbow(num_clusters)

# Now use this data frame and custom color set for the ggplot2 call
plot_gmm_2d <- ggplot(clustering_data_df, aes(x = rating, y = discounted_price, color = as.factor(clusters))) +
  geom_point(alpha = 0.6) +
  labs(title = "2D Scatter Plot of GMM Clusters",
       x = "Scaled Rating",
       y = "Scaled Discounted Price") +
  theme_minimal() +
  scale_color_manual(values = colors) +
  theme(legend.title = element_blank())

# Display the 2D scatter plot
print(plot_gmm_2d)


```





